Research log

### 2024-01-07 docs/ExploratoryResults.Rmd
fixed a typo

E4.misses_per_word %>%
  ggplot(aes(x=nonpretend,y=pretend, label=toupper(word))) +
  geom_abline(intercept=0,slope=1) +
  geom_point()+
  geom_text_repel()+
  coord_fixed(ratio=1)+
  scale_x_continuous(limits=c(0,5), breaks=seq(0,5))+
  scale_y_continuous(limits=c(0,5), breaks=seq(0,5)) +
  theme(legend.position = 'none')+
  theme_bw() +
  labs(x='median number of misses: non-pretend',
       y='median number of misses: pretend')

@@

Among simulators, pretend games were significantly more optimal than non-pretend games (`r apa_print(E4.sim.mean_P_click_rank%>%spread(test_part,p_click_rank)%>%mutate(diff=pretend-random)%>%pull(diff)%>%t.test())$full_result`) even when restricting the analysis to letter selections that resulted in a miss (`r apa_print(E4.sim.mean_P_click_rank_misses_only%>%spread(test_part,p_click_rank)%>%mutate(diff=pretend-random)%>%pull(diff)%>%t.test())$full_result`). Like in the full sapmle, simulators were more optimal when playing normally than when pretending (`r apa_print(E4.sim.mean_P_click_rank%>%spread(test_part,p_click_rank)%>%mutate(diff=pretend-nonpretend)%>%pull(diff)%>%t.test())$full_result`), also when focusing on misses (`r apa_print(E4.sim.mean_P_click_rank_misses_only%>%spread(test_part,p_click_rank)%>%mutate(diff=pretend-nonpretend)%>%pull(diff)%>%t.test())$full_result`).

>>>>

E4.misses_per_word %>%
  ggplot(aes(x=nonpretend,y=pretend, label=toupper(word))) +
  geom_abline(intercept=0,slope=1, color='lightgray') +
  geom_point()+
  geom_text_repel()+
  coord_fixed(ratio=1)+
  scale_x_continuous(limits=c(0,5), breaks=seq(0,5))+
  scale_y_continuous(limits=c(0,5), breaks=seq(0,5)) +
  theme(legend.position = 'none')+
  theme_bw() +
  labs(x='median number of misses: non-pretend',
       y='median number of misses: pretend')

@@

Among simulators, pretend games were significantly more optimal than random (`r apa_print(E4.sim.mean_P_click_rank%>%spread(test_part,p_click_rank)%>%mutate(diff=pretend-random)%>%pull(diff)%>%t.test())$full_result`) even when restricting the analysis to letter selections that resulted in a miss (`r apa_print(E4.sim.mean_P_click_rank_misses_only%>%spread(test_part,p_click_rank)%>%mutate(diff=pretend-random)%>%pull(diff)%>%t.test())$full_result`). Like in the full sapmle, simulators were more optimal when playing normally than when pretending (`r apa_print(E4.sim.mean_P_click_rank%>%spread(test_part,p_click_rank)%>%mutate(diff=pretend-nonpretend)%>%pull(diff)%>%t.test())$full_result`), also when focusing on misses (`r apa_print(E4.sim.mean_P_click_rank_misses_only%>%spread(test_part,p_click_rank)%>%mutate(diff=pretend-nonpretend)%>%pull(diff)%>%t.test())$full_result`).
